The Post-2007 Declining U.S. Birth Rates imply Significant Societal Shifts in the U.S.

### 2023-02-23 outputs/paper/paper.qmd
Update paper.qmd

fig1_data %>%
  ggplot(aes(x = year,
             y = brate_all)) +
  geom_line() +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  labs(
    title = "Trend in US Birth Rates",
    x = "Years",
    y = "Births per 1,000 women age 15-44",
    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
  )  +  
  geom_vline(xintercept = 2007, linetype = "dashed") +
  geom_text(aes(x = 2007, y = 70), nudge_x = 2, nudge_y = 1, label = "2007") +
  theme_light()
```

>>>>

fig1_data <- read.csv(here::here("inputs/data/fig_1.csv"))
fig1_data %>%
  ggplot(aes(x = year,
             y = brate_all)) +
  geom_line() +
  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
  labs(
    title = "Trend in US Birth Rates",
    x = "Years",
    y = "Births per 1,000 women age 15-44",
    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
  )  +  
  geom_vline(xintercept = 2007, linetype = "dashed") +
  geom_text(aes(x = 2007, y = 70), nudge_x = 2, nudge_y = 1, label = "2007") +
  theme_light()
```
